### 2018-05-22 response-two.tex

\comment{3}{%
Line 165. ``Alright'' is not quite the right word here. I think you mean either acceptable or reasonable. Did you consider other options, such as using only one component for one velocity model? I assume that you wanted as large a dataset as possible, but you should state the reason you followed the approach of using all data.
}

\response{%
Certainly. We fixed the language and added a sentence to explain the reason behind our choice, which was indeed to use a dataset as large as possible. Thank you.
}

\comment{4}{%
Figure 5. Consider adding lines to each plot that would indicate a 1:1 relation between the x and y axes. These lines would highlight datasets that lie on and off this line, as well as help the reader better see the scatter in the data.
}

\response{%
We appreciate this comment. However, we are reluctant to add the 1:1 relationship lines. The reason being that these plots should not be interpreted as typical correlation plots of scattered data are usually interpreted. If we add the line we would be erroneously leading the readers to think these are as any other $x$-$y$ plots showing the relationship of two metrics as seen through the data. Here, one also needs to understand that the symbols (or colors) and how well defined are the transitions from one to another are actually equally, and perhaps more important than whether the cloud of data points follow a 1:1 relationship or not. We will therefore appreciate it if we can leave the figure as is, and instead, we added a short sentence to make this point clearer to the reader on page 15, lines 347--349.
}

### 2018-05-22 results.tex
completed second review

Some aspects of Fig.~\ref{fig:clusters} are worth discussing. Although in most plots all four clusters are clearly distinguishable, there are others in which that is not the case. In the combinations in the 3-feature analysis, for instance, the excellent cluster has a limited presence. This is due to the influence of the lower C9 values (see Fig.~\ref{fig:data-box-plot}) on the correlations with C5 and C7. This is not necessarily a bad thing, as it helps to understand the different relationships between the various GOF metrics. In the best of cases, the combinations C1-C2 and C5-C8 in the 2- and 4-feature analysis, for instance, exhibit an almost perfect proportionality between the metrics. That means either one of the metrics in those combinations is redundant. Relationships with redundant features are those where knowledge about one of the features provides a direct view into the other. On the other hand, the combination C1-C7 in the 2-feature analysis presents an example of an irrelevant feature. We say C1 is irrelevant because it provides no insight about the outcome of C7 or that of the clusters. Identifying subspaces with redundant and irrelevant features is important because, on the one hand, the former help reduce the number of necessary features, while on the other hand, the latter can essentially be discarded because of their weak contribution to the decision making process \citep{Dy_2004_MLR}.

@@

Based on these criteria, we selected three candidate trees: T1, T2, and T3. These trees are shown in Fig.~\ref{fig:trees}. T1 is the simplest of the three, and T2 and T3 share some of their topology on the right-hand side. T3 is the most complex of them. More complex trees tend to be deeper, have more nodes, and employ more attributes, all of which depends---in part---on the pruning process. More complex trees have higher $F_1$ values, but they may not necessarily be more practical. In total T1, T2, and T3 use 2, 3 and 4 attributes respectively. All coincide in the use of the C4 (total energy) and C8 (response spectra) as key metrics. T2 adds C5 (peak acceleration), and T3 adds C6 (peak velocity) to the previous metrics.

@@

The results in Table 6 highlight the fact that, for all trees, the metrics \change{C4 (total energy) and C8 (response spectra) are consistently the most relevant ones in the decision algorithms. They are followed by C5 (peak acceleration) and C6 (peak velocity). On the other end, C11 (strong phase duration) plays no role whatsoever in any of the trees, and that C1 (Arias integral), C2 (energy integral), and C3 (Arias intensity) have only small to marginal participations. The remaining metrics---C7 (peak displacement), C9 (Fourier spectrum), and C10 (cross correlation)}---have a somewhat significant participation, but only in the more complex trees.

An additional aspect worth highlighting here is the fact that the clustering and decision tree processes address the problem of correlation between the metrics in a natural way. For instance, one would expect \change{C3 (Arias intensity) and C5 (peak acceleration), or C3 and C4 (total energy)} to be related. Considering them all without distinction could lead to double weighing their influence, and assuming a 1-to-1 relationship may overstate their level of correlation. Instead, the process used here determines which of them has a better chance to predict the outcome in the presence of the other, and preserves that metric as part of the decision tree.

One can put this to test by removing one or more metrics and see how the participation of the metrics rearranges. Table \ref{tab:participation-extra} shows these participations for trees with similar topologies (i) when removing \change{C8 (response spectrum), and (ii) when removing C5 (peak acceleration) and C8. In the first case, C5 takes the place of the most determinant metric, followed by C4 (total energy) and C6 (peak velocity), depending on the tree. In the second case, C6 becomes the most dominant, followed by C3 (Arias intensity) and C4, which vary in their level of participation depending on the tree. These additional alternatives emphasizes the C4 and C6, and show that other metrics such as C5, C7 (peak displacement) and C9 (Fourier spectrum) are also relevant. They also reaffirm the low or null levels of contribution of metrics C1 (Arias integral), C2 (energy integral), C10 (cross correlation) and C11 (strong phase duration)}. All this is consistent with what we observed in Fig.~\ref{fig:boxed-clusters}.

That being said, a low participation does not necessarily mean that a given metric is not relevant at all. Arguably, the strong phase duration is highly regarded as an important parameter for strong motion records in engineering. What the results we present here mean is that, in the context of this particular set of 11 metrics, in order to classify whether a simulation result is poor, fair, good, or excellent, other metrics such as \change{C4 (energy) are much more influential in the final result than C11 (strong phase duration)}. This, of course, is done under the assumption that one seeks to narrow the selection of metrics without loss of insight about the outcome of the validation process when compared to the outcome obtained with the whole suite of the eleven metrics used here.

In the end, the final selection of a preferred tree comes down to reducing complexity in the analysis without compromising the interpretation of results. We favor tree T1 because it is based only on three decision steps, and two GOF metrics: \change{C4 (total energy), and C8 (response spectra)}.

>>>>

Some aspects of Fig.~\ref{fig:clusters} are worth discussing. \change{First of all, one must keep in mind that these are not typical correlation plots. How well defined the clusters are from each other or with respect to the metrics are important aspects to consider.} Although in most plots all four clusters are clearly distinguishable, there are others in which that is not the case. In the combinations in the 3-feature analysis, for instance, the excellent cluster has a limited presence. This is due to the influence of the lower C9 values (see Fig.~\ref{fig:data-box-plot}) on the correlations with C5 and C7. This is not necessarily a bad thing, as it helps to understand the different relationships between the various GOF metrics. In the best of cases, the combinations C1-C2 and C5-C8 in the 2- and 4-feature analysis, for instance, exhibit an almost perfect proportionality between the metrics. That means either one of the metrics in those combinations is redundant. Relationships with redundant features are those where knowledge about one of the features provides a direct view into the other. On the other hand, the combination C1-C7 in the 2-feature analysis presents an example of an irrelevant feature. We say C1 is irrelevant because it provides no insight about the outcome of C7 or that of the clusters. Identifying subspaces with redundant and irrelevant features is important because, on the one hand, the former help reduce the number of necessary features, while on the other hand, the latter can essentially be discarded because of their weak contribution to the decision making process \citep{Dy_2004_MLR}.

@@

Based on these criteria, we selected three candidate trees: T1, T2, and T3. These trees are shown in Fig.~\ref{fig:trees}. T1 is the simplest of the three, and T2 and T3 share some of their topology on the right-hand side. T3 is the most complex of them. More complex trees tend to be deeper, have more nodes, and employ more attributes, all of which depends---in part---on the pruning process. More complex trees have higher $F_1$ values, but they may not necessarily be more practical. In total T1, T2, and T3 use 2, 3 and 4 attributes respectively. All coincide in the use of \change{the total energy (C4) and response spectra (C8) as key metrics. T2 adds the peak acceleration (C5), and T3 adds the peak velocity (C6)} to the previous metrics.

@@

The results in Table 6 highlight the fact that, for all trees, the metrics \change{for total energy (C4) and response spectra (C8) are consistently the most relevant ones in the decision algorithms. They are followed by the peak acceleration (C5) and peak velocity (C6). On the other end, the strong phase duration (C11) plays no role whatsoever in any of the trees, and the Arias integral (C1), energy integral (C2), and Arias intensity (C3) have only small to marginal participations. The remaining metrics---peak displacement (C7), Fourier spectrum (C9), and cross correlation (C10)}---have a somewhat significant participation, but only in the more complex trees.

An additional aspect worth highlighting here is the fact that the clustering and decision tree processes address the problem of correlation between the metrics in a natural way. For instance, one would expect \change{the Arias intensity (C3) and peak acceleration (C5), or the Arias intensity (C3) and total energy (C4)} to be related. Considering them all without distinction could lead to double weighing their influence, and assuming a 1-to-1 relationship may overstate their level of correlation. Instead, the process used here determines which of them has a better chance to predict the outcome in the presence of the other, and preserves that metric as part of the decision tree.

One can put this to test by removing one or more metrics and see how the participation of the metrics rearranges. Table \ref{tab:participation-extra} shows these participations for trees with similar topologies (i) when removing \change{the response spectrum (C8), and (ii) when removing both the peak acceleration (C5) and the response spectrum (C8). In the first case, the peak acceleration (C5) takes the place of the most determinant metric, followed by the total energy (C4) and peak velocity (C6), depending on the tree. In the second case, the peak velocity (C6) becomes the most dominant, followed by the Arias intensity (C3) and the total energy (C4), which vary in their level of participation depending on the tree. These additional alternatives emphasize the role of the total energy (C4) and the peak velocity (C6), and show that other metrics such as the peak acceleration (C5), peak displacement (C7) and Fourier spectrum (C9) are also relevant. They also reaffirm the low or null levels of contribution of the metrics associated with the shape of the Arias integral (C1), the energy integral (C2), and the cross correlation (C10) and strong phase duration (C11)}. All this is consistent with what we observed in Fig.~\ref{fig:boxed-clusters}.

That being said, a low participation does not necessarily mean that a given metric is not relevant at all. Arguably, the strong phase duration is highly regarded as an important parameter for strong motion records in engineering. What the results we present here mean is that, in the context of this particular set of 11 metrics, in order to classify whether a simulation result is poor, fair, good, or excellent, other metrics such as \change{the total energy (C4) are much more influential in the final result than the strong phase duration (C11)}. This, of course, is done under the assumption that one seeks to narrow the selection of metrics without loss of insight about the outcome of the validation process when compared to the outcome obtained with the whole suite of the eleven metrics used here.

In the end, the final selection of a preferred tree comes down to reducing complexity in the analysis without compromising the interpretation of results. We favor tree T1 because it is based only on three decision steps, and two GOF metrics: \change{the total energy (C4) and response spectra (C8)}.
